Cassini State Capture

### 2019-10-10 writeups/Su_disk_disp.tex
oops needed to address a few more TODOs

    \item $III \to III$ only, $A_i > \max A_I + A_{II}$.
\end{itemize}
\begin{figure}
    \centering
    \begin{subfigure}{\columnwidth}
        \centering
        \includegraphics[width=\columnwidth]{../initial/2_toy2/3testo21.png}
    \end{subfigure}
    \begin{subfigure}{\columnwidth}
        \centering
        \includegraphics[width=\columnwidth]{../initial/2_toy2/3testo21_subplots.png}
    \end{subfigure}
    \caption{Fiducial simulation following the $A_{II} \to A_{I}$ transition.
    Top plot upper panel: plot of $\cos \theta(t)$ (gold) in an example
    simulation. Overlaid are the locations of Cassini State 2 (magenta), and
    upper and lower bounds on the separatrix (black). Note that the trajectory
    successfully tracks CS2 to a misalignment angle $\theta \approx 90^\circ$.
    Vertical green lines denote times portrayed in bottom plot. Top plot lower
    panel: plot of the enclosed separatrix area obtained by integrating the
    simulated trajectory (blue dots) and adiabatic theory (red line). Lower
    plot: snapshots in the $\p{\cos \theta, \phi}$ space of the simulation
    trajectories for the times demarcated in green above, corresponding to the
    start of the simulation, the appearance of the separatrix, two panels
    depicting the separatrix crossing process, and a final snapshot at $\eta =
    10^{-3.5}$. Gold dots denote a full circulation or libration cycle at the
    selected time, while the separatrix at the start/end of the portrayed cycle
    are shown in solid/dashed black lines respectively. Also labeled is CS2
    (magenta). Finally, the enclosed phase space area is shaded in grey ($A >
    0$) and red ($A < 0$).}\label{fig:ad_21}
\end{figure}
\begin{figure}
    \centering
    \begin{subfigure}{\columnwidth}
        \centering
        \includegraphics[width=\columnwidth]{../initial/2_toy2/3testo23.png}
    \end{subfigure}
    \begin{subfigure}{\columnwidth}
        \centering
        \includegraphics[width=\columnwidth]{../initial/2_toy2/3testo23_subplots.png}
    \end{subfigure}
    \caption{Same as \autoref{fig:ad_21} but for the $A_2 \to A_3$ track.
    }\label{fig:ad_23}
\end{figure}
\begin{figure}
    \centering
    \begin{subfigure}{\columnwidth}
        \centering
        \includegraphics[width=\columnwidth]{../initial/2_toy2/3testo31.png}
    \end{subfigure}
    \begin{subfigure}{\columnwidth}
        \centering
        \includegraphics[width=\columnwidth]{../initial/2_toy2/3testo31_subplots.png}
    \end{subfigure}
    \caption{Same as \autoref{fig:ad_21} but for the $A_{III} \to A_I$
    track.}\label{fig:ad_31}
\end{figure}
\begin{figure}
    \centering
    \begin{subfigure}{\columnwidth}
        \centering
        \includegraphics[width=\columnwidth]{../initial/2_toy2/3testo321.png}
    \end{subfigure}
    \begin{subfigure}{\columnwidth}
        \centering
        \includegraphics[width=\columnwidth]{../initial/2_toy2/3testo321_subplots.png}
    \end{subfigure}
    \caption{Same as \autoref{fig:ad_21} but for the $A_{III} \to A_{II} \to A_I$
    track. Two separatrix crossings are shown.}\label{fig:ad_321}
\end{figure}

@@

Next, we will consider the evolution of a system with arbitrary $\theta_{sd, i}$
starting in the $\eta \gg 1$ regime. By evolving such systems until $\eta \ll
1$, we can measure the final $\theta_f$ values and make comparisons with those
obtained via the dynamical tracks above. Observe that when $\eta \gg 1$,
trajectories librate with approximately constant $\theta_{sd}$, meaning they
enclose phase space area
\begin{equation}
    A_i = 2\pi\p{1 - \cos \theta_{sd, i}}.\label{eq:ai_qsd}
\end{equation}
Thus, for a given $\theta_{sd, i}$, we know immediately which tracks are
accessible and with what probability following the results of
\autoref{ss:zone_transitions}.

We run simulations over a ring of initial conditions at each $\theta_{sd, i}$
and measure the final $\theta_{f}$ values. We use \autoref{eq:ai_qsd} to predict
the final obliquities $\theta_f$ according to each of the dynamical tracks. The
agreement of these predictions for $I = 5^\circ, 10^\circ, 20^\circ$ can be seen
in \autoref{fig:ad_ensemble}, \autoref{fig:3_ensemble_10_35}, and
\autoref{fig:3_ensemble_20_35}.
\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{../initial/2_toy2/3_ensemble_05_35.png}
    \caption{Top: $\theta_{f}\p{\theta_{sd, i}}$, overlaid with semi-analytic
    predictions of the $\theta_{ f}$ for each of the four nontrivial
    dynamical tracks in colored lines. Bottom: Semi-analytic probabilities of
    each of the dynamical tracks for each $\theta_{sd, i}$. The five regimes of
    $\theta_{sd, i}$ values correspond to the five regimes of $A_i$ discussed in
    \autoref{ss:zone_transitions} when using \autoref{eq:ai_qsd} to relate
    $A_i\p{\theta_{sd, i}}$. }\label{fig:ad_ensemble}
\end{figure}
\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{../initial/2_toy2/3_ensemble_10_35.png}
    \caption{Same as \autoref{fig:ad_ensemble} but for $I =
    10^\circ$.}\label{fig:3_ensemble_10_35}
\end{figure}
\begin{figure}
    \includegraphics[width=\columnwidth]{../initial/2_toy2/3_ensemble_20_35.png}
    \caption{Same as \autoref{fig:ad_ensemble} but for $I =
    10^\circ$.}\label{fig:3_ensemble_20_35}
\end{figure}

>>>>

    \item $III \to III$ only, $A_i > \max A_I + A_{II}$.
\end{itemize}
\begin{figure}
    \centering
    \begin{subfigure}{\columnwidth}
        \centering
        \includegraphics[width=\columnwidth]{../initial/2_toy2/3testo21.png}
    \end{subfigure}
    \begin{subfigure}{\columnwidth}
        \centering
        \includegraphics[width=\columnwidth]{../initial/2_toy2/3testo21_subplots.png}
    \end{subfigure}
    \caption{Fiducial simulation following the $A_{II} \to A_{I}$ transition. An
    initial $\theta_{sd, i} = 0.3\;\mathrm{rad} \approx 17.2^\circ$ was used, as
    well as $\epsilon = 3 \times 10^{-4}$. Top plot upper panel: plot of $\cos
    \theta(t)$ (gold) in an example simulation. Overlaid are the locations of
    Cassini State 2 (magenta), and upper and lower bounds on the separatrix
    (black). Note that the trajectory successfully tracks CS2 to a misalignment
    angle $\theta \approx 90^\circ$. Vertical green lines denote times portrayed
    in bottom plot. Top plot lower panel: plot of the enclosed separatrix area
    obtained by integrating the simulated trajectory (blue dots) and adiabatic
    theory (red line). Lower plot: snapshots in the $\p{\cos \theta, \phi}$
    space of the simulation trajectories for the times demarcated in green
    above, corresponding to the start of the simulation, the appearance of the
    separatrix, two panels depicting the separatrix crossing process, and a
    final snapshot at $\eta = 10^{-3.5}$. Gold dots denote a full circulation or
    libration cycle at the selected time, while the separatrix at the start/end
    of the portrayed cycle are shown in solid/dashed black lines respectively.
    Also labeled is CS2 (magenta). Finally, the enclosed phase space area is
    shaded in grey ($A > 0$) and red ($A < 0$).}\label{fig:ad_21}
\end{figure}
\begin{figure}
    \centering
    \begin{subfigure}{\columnwidth}
        \centering
        \includegraphics[width=\columnwidth]{../initial/2_toy2/3testo23.png}
    \end{subfigure}
    \begin{subfigure}{\columnwidth}
        \centering
        \includegraphics[width=\columnwidth]{../initial/2_toy2/3testo23_subplots.png}
    \end{subfigure}
    \caption{Same as \autoref{fig:ad_21} but for the $A_2 \to A_3$ track.
    $\theta_{sd, i} = 0.3\;\mathrm{rad} \approx 17.2^\circ$, and $\epsilon =
    3.01 \times 10^{-4}$.}\label{fig:ad_23}
\end{figure}
\begin{figure}
    \centering
    \begin{subfigure}{\columnwidth}
        \centering
        \includegraphics[width=\columnwidth]{../initial/2_toy2/3testo31.png}
    \end{subfigure}
    \begin{subfigure}{\columnwidth}
        \centering
        \includegraphics[width=\columnwidth]{../initial/2_toy2/3testo31_subplots.png}
    \end{subfigure}
    \caption{Same as \autoref{fig:ad_21} but for the $A_{III} \to A_I$
    track. $\theta_{sd, i} = 89.1^\circ$, and $\epsilon = 3.01 \times
    10^{-4}$.}\label{fig:ad_31}
\end{figure}
\begin{figure}
    \centering
    \begin{subfigure}{\columnwidth}
        \centering
        \includegraphics[width=\columnwidth]{../initial/2_toy2/3testo321.png}
    \end{subfigure}
    \begin{subfigure}{\columnwidth}
        \centering
        \includegraphics[width=\columnwidth]{../initial/2_toy2/3testo321_subplots.png}
    \end{subfigure}
    \caption{Same as \autoref{fig:ad_21} but for the $A_{III} \to A_{II} \to A_I$
    track. $\theta_{sd, i} = 60^\circ$, and $\epsilon = 3.14 \times 10^{-4}$.
    Two separatrix crossings are shown.}\label{fig:ad_321}
\end{figure}

@@

Next, we will consider the evolution of a system with arbitrary $\theta_{sd, i}$
starting in the $\eta \gg 1$ regime. By evolving such systems until $\eta \ll
1$, we can measure the final $\theta_f$ values and make comparisons with those
obtained via the dynamical tracks above. Observe that when $\eta \gg 1$,
trajectories librate about $\hat{l}_d$, or equivalently CS2, with approximately
constant $\theta_{sd}$, meaning they enclose phase space area
\begin{equation}
    A_i = 2\pi\p{1 - \cos \theta_{sd, i}}.\label{eq:ai_qsd}
\end{equation}
Thus, for a given $\theta_{sd, i}$, we know immediately which tracks are
accessible and with what probability following the results of
\autoref{ss:zone_transitions}.

We run simulations over a ring of initial conditions at each $\theta_{sd, i}$
and measure the final $\theta_{f}$ values. Since we start with finite $\eta$, we
use the angular distance to CS2 as a proxy for $\theta_{sd, i}$, as it is the
correct quantity to use to make \autoref{eq:ai_qsd} hold exactly. We use
\autoref{eq:ai_qsd} to predict the final obliquities $\theta_f$ according to
each of the dynamical tracks. The agreement of these predictions for $I =
5^\circ, 10^\circ, 20^\circ$ can be seen in \autoref{fig:ad_ensemble},
\autoref{fig:3_ensemble_10_35}, and \autoref{fig:3_ensemble_20_35}.
\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{../initial/2_toy2/3_ensemble_05_35.png}
    \caption{Top: $\theta_{f}\p{\theta_{sd, i}}$, overlaid with semi-analytic
    predictions of the $\theta_{ f}$ for each of the four nontrivial
    dynamical tracks in colored lines. Bottom: Semi-analytic probabilities of
    each of the dynamical tracks for each $\theta_{sd, i}$. The five regimes of
    $\theta_{sd, i}$ values correspond to the five regimes of $A_i$ discussed in
    \autoref{ss:zone_transitions} when using \autoref{eq:ai_qsd} to relate
    $A_i\p{\theta_{sd, i}}$. }\label{fig:ad_ensemble}
\end{figure}
\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{../initial/2_toy2/3_ensemble_10_35.png}
    \caption{Same as \autoref{fig:ad_ensemble} but for $I =
    10^\circ$.}\label{fig:3_ensemble_10_35}
\end{figure}
\begin{figure}
    \includegraphics[width=\columnwidth]{../initial/2_toy2/3_ensemble_20_35.png}
    \caption{Same as \autoref{fig:ad_ensemble} but for $I =
    10^\circ$.}\label{fig:3_ensemble_20_35}
\end{figure}
